A Constraint Solving Approach to Parikh Images of Regular Languages

### 2024-03-06 conclusion.tex
meta-data

The second track for future improvements is the extension into other problem
domains, including other logics, model checking problems, as well as to more
powerful automata such as transducers. In principle, we are also already able to
express stronger constraints than Parikh automata due to our use of a full
automated theorem prover, which allows adding arbitrary constraints in addition
to the expected Presburger formulae.

>>>>

The second track for future improvements is the extension into other problem
domains, including other logics, model checking problems, as well as to more
powerful automata such as transducers. In principle, we can already express
stronger constraints than Parikh automata due to our use of an automated theorem
prover which allows rich constraints on counter variables.

\begin{acks}
  This work was supported by
    the Swedish Research Council (VR)
    under grant~2018-04727, the Swedish Foundation for Strategic
    Research (SSF) under the project WebSec (Ref.\ RIT17-0011), and the
    Wallenberg project UPDATE.
\end{acks}

### 2024-03-06 main.tex
Fix units, mention SMT-COMP results in abstract
Data statement
meta-data

\usepackage{amsmath,empheq,fancybox}
\usepackage{paralist}
\usepackage{url}
\usepackage{color}
\usepackage{textcomp,listings}
\usepackage{array}
\usepackage{mymacros}
\usepackage{microtype}
\usepackage{listings}
\usepackage{csquotes}
\usepackage{proof}
\usepackage[capitalise]{cleveref}
\usepackage{algorithm2e}      
\usepackage{multirow}
\usepackage{mathpartir}
\usepackage{amsthm}
\usepackage{numprint}
\usepackage{ebproof}
\usepackage[makeroom]{cancel}

@@

%% Author with single affiliation.
\author{Amanda Stjerna}
%\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
\orcid{0000-0003-4180-6118}             %% \orcid is optional
\affiliation{
  %\position{Position1}
  \department{Department of Information Technology}              %% \department is recommended
  \institution{Uppsala university}            %% \institution is required
  \streetaddress{Lägerhyddsvägen 1, hus 10}
  \city{Uppsala}
  \country{Sweden}                    %% \country is recommended
}
\email{amanda.stjerna@it.uu.se}          %% \email is recommended

%% Author with two affiliations and emails.
\author{Philipp Rümmer}
%\authornote{with author2 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
\orcid{0000-0002-2733-7098}             %% \orcid is optional
\affiliation{
  \position{Position2a}
  \department{Department2a}             %% \department is recommended
  \institution{Institution2a}           %% \institution is required
  \streetaddress{Street2a Address2a}
  \city{City2a}
  \state{State2a}
  \postcode{Post-Code2a}
  \country{Country2a}                   %% \country is recommended
}
\email{first2.last2@inst2a.com}         %% \email is recommended
\affiliation{
  \position{Position2b}
  \department{Department2b}             %% \department is recommended
  \institution{Institution2b}           %% \institution is required
  \streetaddress{Street3b Address2b}
  \city{City2b}
  \state{State2b}
  \postcode{Post-Code2b}
  \country{Country2b}                   %% \country is recommended
}
\email{first2.last2@inst2b.org}         %% \email is recommended

@@

@@

%% Appendix
\appendix
\section{Appendix}
\input{appendix.tex}
\end{document}

>>>>

\usepackage{amsmath,empheq,fancybox}
\usepackage{paralist}
\usepackage{url}
\usepackage{color}
\usepackage{textcomp,listings}
\usepackage{array}
\usepackage{mymacros}
\usepackage{microtype}
\usepackage{listings}
\usepackage{csquotes}
\usepackage{proof}
\usepackage[capitalise]{cleveref}
\usepackage{algorithm2e}      
\usepackage{multirow}
\usepackage{mathpartir}
\usepackage{amsthm}
\usepackage{numprint}
\usepackage{ebproof}
\usepackage{siunitx}
\usepackage[makeroom]{cancel}

@@

%% Author with single affiliation.
\author{Amanda Stjerna}
%\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
\orcid{0000-0003-4180-6118}             %% \orcid is optional
\affiliation{
  %\position{Position1}
  \department{Department of Information Technology}              %% \department is recommended
  \institution{Uppsala University}            %% \institution is required
  \streetaddress{Lägerhyddsvägen 1, hus 10}
  \city{Uppsala}
  \country{Sweden}                    %% \country is recommended
}
\email{amanda.stjerna@it.uu.se}          %% \email is recommended

%% Author with two affiliations and emails.
\author{Philipp Rümmer}
%\authornote{with author2 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
\orcid{0000-0002-2733-7098}             %% \orcid is optional
\affiliation{
%  \position{Position2a}
  \department{Faculty of Informatics and Data Science}             %% \department is recommended
  \institution{University of Regensburg}           %% \institution is required
  \streetaddress{Bajuwarenstraße 4}
  \city{Regensburg}
  \postcode{93053}
  \country{Germany}                   %% \country is recommended
}
\email{philipp.ruemmer@ur.de}         %% \email is recommended
\affiliation{
  %\position{Position1}
  \department{Department of Information Technology}              %% \department is recommended
  \institution{Uppsala University}            %% \institution is required
  \streetaddress{Lägerhyddsvägen 1, hus 10}
  \city{Uppsala}
  \country{Sweden}                    %% \country is recommended
}
\email{philipp.ruemmer@it.uu.se}         %% \email is recommended

@@

%% Appendix
\appendix
\section{Appendix}
\input{appendix.tex}

\section{Data-Availability Statement}
\input{data.tex}

@@

\end{document}
